Cognitive Context: Impact on the Perception of a Robot

### 2015-10-29 main.tex
Do not mention participants came only once

The study lasted about 15 minutes per participant; each participant was invited
for one session only.

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
condition was between-subject ( 30 subjects performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 56 participants).

>>>>

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
condition was between-subject (30 subjects performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 56 participants). The study lasted in average 15
minutes per participant.
